\papertitle

### 2012-10-13 manuscript.tex

\begin{figure}[tb]
\centering
\includegraphics[width=\linewidth]{figures/block_diagrams.pdf}
\caption{Overall block diagram of the cooperative control system.}
\label{fig:block_diagram}
\end{figure}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{System Model}
\label{sec:system_model}

@@

To model the translational position of the ornithopter, we use a form of Dubin's car model (Eq.~\ref{eq:total_model_plain})~\cite{lavalle:planning}. 
\begin{equation}
\label{eq:total_model_plain}
\begin{aligned}
& \dot{x} = sin(\theta)\\
& \dot{y} = cos(\theta)\\
\end{aligned}
\end{equation}
Our form uses the angular position, $\theta$ as an input rather than a state. We model the overall motion of the system as shown in Equation~\ref{eq:total_model_plain}, where $\theta$ is the time domain output of (Eq. \ref{eq:plain_model}) with the reference heading angle as the input.

@@

 We model the 
viewing angle of the camera as a pixel map from one edge of a
63$^{\circ}$ viewing triangle to the other. The camera has an image width of
640 pixels. We calculate the desired heading angle in degrees for a given distance from the
camera according to Equation~\ref{eq:desired_heading}, where $d$
is the distance between the ornithopter and the camera, and $x$ is the horizontal
position of the robot relative to the center of the window in meters. This
explicitly fact that the pose estimation algorithm does not estimate the depth of the
robot.
\begin{equation} \label{eq:desired_heading} \text{Desired heading} =
\frac{640\text{px}}{2*\text{d}*\tan{\frac{63^{\circ}}{2}}}*\frac{63^{\circ}}{640\text{px}}*\text{x}
\end{equation}

@@

We performed each trial as follows (see Fig.~\ref{fig:pf_screencap}):
\begin{enumerate}
\item The window is identified by the user. 
\item We release H$^2$Bird by hand, in view of the camera at the desired starting grid point.
\item The H$^2$Bird attempts to fly through the window with, with remote guidance from
the ground station.
\end{enumerate}

@@

\begin{figure}[tb]
\centering
\includegraphics[width=\linewidth]{figures/experiment_cartoon.pdf}
\caption{Conceptual sketch of experimental setup.}
\label{fig:experiment_cartoon}
\end{figure}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Results and Performance}
\label{sec:performance}
To bound the performance of the cooperative control system, we determine 
the feasible set of initial conditions that result in successful narrow 
passage traversal, using both analytical and empirical methods. We then conducts 
experiments to validate this model.

@@

%............................................................................%
\subsubsection{Ornithoper Attitude Control}
\label{sec:flight_control}
\begin{figure}[tb]
\centering
\includegraphics[width=\linewidth]{figures/step_response_total.pdf}
\caption{H$^2$Bird step response}
\label{fig:step_response}
\end{figure}
%TODO reduce number of sig figs

The results of the step response experiment are described in
Fig.~\ref{fig:step_response}. The first-order model that we fit to the
response is in Equation~\ref{eq:transfer_func}.

@@

We present the results of our experimental trials in
Figs.~\ref{fig:flight_paths} and~\ref{fig:flight_paths_feasible}. For
initial conditions in the middle of the testing space and in front of the
camera, we achieved a success rate of 80\%. This case is depicted in
Fig.~\ref{fig:flight_paths_feasible}. As we moved towards the edges of the
feasible region in Fig.~\ref{fig:flight_paths}, the success rate diminishes
to 50\% because of several factors. On the edges of the camera frame, the yaw
control inputs are large in magnitude, although this is not necessary in all
cases. Since the control algorithm we are using has no notion of depth, it
applies the same control input whether the ornithopter is close to the camera,
where small changes in heading are adequate, or far away from the camera,
where large changes in heading are necessary. Due to this phenomenon, the
controller often over or under-compensates in certain regions, depending upon
the PID tuning and the distance from the camera. Tracking noise can also cause
passage negotiation to fail. Variations in the H$^2$Bird hand launch can cause
the system to respond differently for similar initial conditions. In addition,
the H$^2$Bird battery was changed approximately every 5 tests, adding more
variation to the H$^2$Bird performance by affecting the motor power output.

@@

We simulated the motion of the ornithopter, beginning from certain positional
and angular initial conditions using several components representing the
experimental layout of our system described in Fig.~\ref{fig:block_diagram}.
For the ``ornithopter dynamics'' block, we used the translational model
described by~\ref{eq:total_model_plain}, with the angular position model
described by~\ref{eq:transfer_func}. We tuned the PID controller for the
simulation so that paths from known positions looked similar to the behavior
we observed in the experimental data. We also account for the camera capture and
pose estimation delays, and the PID controller sampling rate in the
simulation.

We determine the backwards reachable set of initial states for successful
narrow passage traversal both geometrically and in simulation
(Fig.~\ref{fig:feasible_set}). For the initial conditions, we use a uniform
grid of 0.05 meter increments within the camera viewing region, and an initial
angular position perpendicular to the narrow passage plane. The geometrically
infeasible region is computed using the minimum turning radius and the
geometry of the camera's field-of-view and is indicated in blue. Both the
regions in red and blue indicate the infeasible region determined in
simulation. The feasible region is highlighted in green. A success consisted
of a path that intersects the window at some point and does not leave the
camera viewing triangle. Fig.~\ref{fig:feasible_set} is validated by our
experimental data, as there are no successes within the geometrically
infeasible region. There are a few successes near the boundary of the
infeasible region determined in simulation, but this phenomenon can be
explained by the results in Fig.~\ref{fig:heat_map}.

Fig.~\ref{fig:heat_map} depicts the results of a Monte Carlo method of
simulating possible paths of the H$^2$Bird during our experiments. For each
point within a 0.2 meter grid within the camera viewing triangle, we simulated
10 trials using an initial heading randomly sampled from a uniform
distribution between -90$^{\circ}$ and 90$^{\circ}$. As shown in the figure,
there is a region in the middle with a 100\% probability of success, which is
a subset of the feasible region presented in Fig.~\ref{fig:feasible_set}.
Along the edges of the camera viewing triangle, however, the probability of
success decreases.

>>>>

\begin{figure}[tb]
\centering
\includegraphics[width=\linewidth]{figures/block_diagrams.pdf}
\caption{Overall block diagram of the cooperative control system.}
\label{fig:block_diagram}
\end{figure}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{System Model}
\label{sec:system_model}

@@

\begin{equation}
\label{eq:dubin_car}
\begin{aligned}
& \dot{x} = u_{s}sin(\theta)\\
& \dot{y} = u_{s}cos(\theta)\\
& \dot{\theta} = u\\
& u \in U=[-\tan{\phi_{max}},\tan{\phi_{max}}]
\end{aligned}
\end{equation}

To model the translational position of the ornithopter, we use a form of Dubin's car model (Eq. ~\ref{eq:dubin_car})~\cite{lavalle:planning}, where $\phi_{max}$ is the maximum steering angle and $u_{s}$ is the forward speed. We modify this model to treat the angular position $\theta$ as an input rather than a state. The overall motion of the system can be modeled as shown in Equation~\ref{eq:total_model_plain}, where $\theta$ is the time domain output of (\ref{eq:plain_model}) with the reference heading angle as the input.

Our form uses the angular position, $\theta$ as an input rather than a state. We model the overall motion of the system as shown in Equation~\ref{eq:total_model_plain}, where $\theta$ is the time domain output of (Eq. \ref{eq:plain_model}) with the reference heading angle as the input.

@@

 We model the 
viewing angle of the camera as a pixel map from one edge of a
63$^{\circ}$ viewing triangle to the other. The camera has an image width of
640 pixels. We calculate the desired heading angle in degrees for a given distance from the
camera according to Equation~\ref{eq:desired_heading}, where $d$
is the distance between the ornithopter and the camera, and $x$ is the horizontal
position of the robot relative to the center of the window in meters. This
relation reflects the fact that the camera cannot determine the depth of the
robot. One example of why this is a problem is that if the robot stays at a
constant horizontal distance from the window, but moves closer and closer to
the camera, the directed heading steadily increases even though the robot has
not actually moved farther from the window. This creates tracking problems in
areas close to the camera.

\begin{equation} \label{eq:desired_heading} \text{Desired heading} =
\frac{640\text{px}}{2*\text{d}*\tan{\frac{63^{\circ}}{2}}}*\frac{63^{\circ}}{640\text{px}}*\text{x}
\end{equation}

@@

% TODO clarify or roll into paragraph
Each trial included the following steps:
\begin{enumerate}
\item The window is identified by the user. 
\item We release H$^2$Bird by hand, in view of the camera at the desired starting grid point.
\item The H$^2$Bird attempts to fly through the window with, with remote guidance from
the ground station.
\end{enumerate}

@@

\begin{figure}[tb]
\centering
\includegraphics[width=\linewidth]{figures/experiment_cartoon.pdf}
\caption{Conceptual sketch of experimental setup.}
\label{fig:experiment_cartoon}
\end{figure}
%TODO label experiment cartoon

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Results and Performance}
\label{sec:performance}
%TODO cameron
To bound the performance of the cooperative control system, we determine 
the feasible set of initial conditions that result in successful narrow 
passage traversal using both analytical and empirical methods. We conducted 
experiments to validate this model.

@@

%............................................................................%
\subsubsection{Ornithoper Attitude Control}
\label{sec:flight_control}
%TODO cameron
\begin{figure}[tb]
\centering
\includegraphics[width=\linewidth]{figures/step_response_total.pdf}
\caption{H$^2$Bird step response}
\label{fig:step_response}
\end{figure}
%TODO reduce number of sig figs

The first-order model that we fit to the
step response of the onrithopter yaw motion is in Equation~\ref{eq:transfer_func}. This model represents the tuning dynamics of the ornithopter as well as the PID controller providing inputs to the actuators.
The results of the step response experiment along with the response of the fitted model are depicted in
Fig.~\ref{fig:step_response}.

@@

Conducting the experimental trials as described in Section~\ref{sec:experiments:verification}, we achieved a success rate of 80\% for
initial conditions in the middle of the testing space and in front of the
camera. As we moved towards the edges of the
feasible region in Fig.~\ref{fig:flight_paths}, the success rate diminished
to 50\%. The results of our experimental trials are shown in
Figs.~\ref{fig:flight_paths} and~\ref{fig:flight_paths_feasible}.

The lower success rate on the edges of the camera frame can be explained by several factors. On the edges of the viewing triangle, the yaw
control inputs are large in magnitude, although this is not necessary in all
cases. Since the control algorithm we are using has no notion of depth, it
applies the same control input whether the ornithopter is close to the camera,
where small changes in heading are adequate, or far away from the camera,
where large changes in heading are necessary. Due to this phenomenon, the
controller often over or under-compensates in certain regions, depending upon
the PID tuning and the distance from the camera. Tracking noise can also cause
passage negotiation to fail. Variations in the H$^2$Bird hand launch can cause
the system to respond differently for similar initial conditions. In addition,
the H$^2$Bird battery was changed approximately every 5 tests, adding more
variation to the H$^2$Bird performance by affecting the motor power output.

@@

We simulated the motion of the ornithopter beginning from various positional
and angular heading initial conditions.
We used the model that we determined through system identification (Sec.~\ref{sec:system_model}) using the cooperative control method in Fig.~\ref{fig:block_diagram}.

We determined the backwards reachable set of initial states for successful
narrow passage traversal both geometrically and in simulation
(Fig.~\ref{fig:feasible_set}). In the figure, the blue lines represent the camera viewing triangle, the black line
represents the window, and the black dot represents the camera. For the initial conditions, we used a uniform
grid of 5 cm increments within the camera viewing region, and an initial
angular heading perpendicular to the window plane. A success, or feasible initial condition, consists
of a path that intersects the window at some point and does not leave the
camera viewing triangle, and is indicated in green. The geometrically
infeasible region is computed using the minimum turning radius and the
geometry of the camera's field-of-view and is indicated in blue. The region in red is not geometrically feasible, but is infeasible as a result of the cooperative control simulation dynamics.

Our experimental data validates Fig.~\ref{fig:feasible_set}, as there are no successes within the geometrically
infeasible region. There are a few successes near the boundary of the
infeasible region determined in simulation. While there are successes along the boundary of the camera viewing triangle, there are also many failures. We further explore this behavior using Monte Carlo simulation.

We conducted a Monte Carlo simulation to determine the probability of successful window navigation for a given point within the testing area. Using this information we can make assumptions about ideal starting positions for coopertive control. For each point within a 0.1 meter grid within the camera viewing triangle, we simulated
40 trials using an initial heading randomly sampled from a uniform
distribution between -90$^{\circ}$ and 90$^{\circ}$.
Fig.~\ref{fig:heat_map} depicts the results of the Monte Carlo simulation. As shown in the figure,
there is a region in the middle with a 100\% probability of success, which is
a subset of the feasible region presented in Fig.~\ref{fig:feasible_set}.
Along the edges of the camera viewing triangle, however, the probability of
success decreases.
